---
title: "Luke W. Johnston"
date: "2024-09-30"
date-format: "medium"
listing:
  - id: courses-taken
    template: ejs/dl-entry.ejs
    contents: data/courses-taken.yml
    field-types:
      start-date: date
      end-date: date  
  - id: certificates
    template: ejs/dl-entry.ejs
    contents: data/certificates.yml
    field-types:
      start-date: date
      end-date: date  
  - id: curriculum-development
    template: ejs/dl-entry.ejs
    contents: data/curriculum-development.yml
    field-types:
      start-date: date
      end-date: date  
  - id: supervision
    template: ejs/dl-entry.ejs
    contents: data/supervision.yml
    field-types:
      start-date: date
      end-date: date  
  - id: affiliations
    template: ejs/dl-entry.ejs
    contents: data/affiliations.yml
    field-types:
      start-date: date
      end-date: date  
  - id: outreach
    template: ejs/dl-entry.ejs
    contents: data/outreach.yml
    field-types:
      start-date: date
      end-date: date  
  - id: funding
    template: ejs/dl-entry.ejs
    contents: data/funding.yml
    field-types:
      start-date: date
      end-date: date
  - id: awards
    template: ejs/dl-entry.ejs
    contents: data/awards.yml
    field-types:
      start-date: date
      end-date: date
  - id: committees
    template: ejs/dl-entry.ejs
    contents: data/committees.yml
    field-types:
      start-date: date
      end-date: date
  - id: employment
    template: ejs/dl-entry.ejs
    contents: data/employment.yml
    field-types:
      start-date: date
      end-date: date
  - id: r-packages
    template: ejs/dl-entry.ejs
    contents: data/r-packages.yml
    field-types:
      start-date: date
  - id: teaching
    template: ejs/dl-entry.ejs
    contents: data/teaching.yml
    field-types:
      start-date: date
      end-date: date
  - id: education
    template: ejs/dl-entry.ejs
    contents: data/education.yml
    field-types:
      start-date: date
      end-date: date
    date-format: "YYYY"
---

```{r setup}
#| include: false
devtools::load_all()
library(here)
library(tidyverse)
bib_items <- read_bib_items()
```


{{< fa envelope >}}\ [lwjohnst\@gmail.com](mailto:lwjohnst@gmail.com){.email}
{{< fa brands gitlab >}}\ [`@lwjohnst`](https://gitlab.com/lwjohnst/) 
{{< fa brands github >}}\ [`@lwjohnst86`](https://github.com/lwjohnst86/)
{{< fa brands orcid >}}\ [0000-0003-4169-2616](https://orcid.org/0000-0003-4169-2616)
{{< fa brands linkedin >}}\ [`lwjohnst`](www.linkedin.com/in/lwjohnst) 
{{< fa brands stack-overflow >}}\ [Luke W. Johnston](https://stackoverflow.com/users/2632184)
{{< fa brands stack-exchange >}}\ [Luke W. Johnston](https://stackexchange.com/users/1992995) 

> I am a diabetes epidemiologist, R and Python software developer, teacher of
> modern data science and analysis skills, and open science advocate.

## {{< fa graduation-cap >}} Education

::: {#education}
:::

## {{< fa building-columns >}} Affiliations

::: {#affiliations}
:::

## {{< fa book-open >}} Publications

```{r list-articles}
list_publications(bib_items, "Journal articles")
```

## {{< fa book >}} Books

```{r list-books}
list_publications(bib_items, "Books")
```

## {{< fa comment-dots >}} Presentations

```{r list-presentations}
list_publications(bib_items, "presentations")
```

## {{< fa box-open >}} R packages

::: {#r-packages}
:::

## {{< fa person-chalkboard >}} Teaching

::: {#teaching}
:::

## {{< fa user-group >}} Supervision

::: {#supervision}
:::

## {{< fa book-open-reader >}} Curriculum development

```{r list-curriculum-archived}
list_publications(bib_items, "Curriculum development")
```

### Other Development

::: {#curriculum-development}
:::

## {{< fa users >}} Committees

::: {#committees}
:::

## {{< fa trophy >}} Awards

::: {#awards}
:::

## {{< fa comments-dollar >}} Funding

::: {#funding}
:::

## {{< fa briefcase >}} Employment

::: {#employment}
:::

## {{< fa bullhorn >}} Outreach activities

::: {#outreach}
::: 

## {{< fa certificate >}} Certificates

::: {#certificates}
::: 

## {{< fa school >}} Courses taken

::: {#courses-taken}
::: 

```{=html}
<style>
dl {
  display: block;
}
dd {
  margin-left: 2em;
}
</style>
```
