
```{r, include = FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    warning = FALSE,
    message = FALSE,
    results = "asis",
    comment = ""
)
# library(cv)
library(here)
devtools::load_all()
library(tidyverse)
library(RefManageR)
RefManageR::BibOptions(
    bib.style = "authoryear",
    first.inits = TRUE,
    style = "markdown",
    max.names = Inf,
    sorting = "ydnt"
    # no.print.fields = NULL
)
cv_data <- read_cv_items() 
bib_items <- read_bib_items() 
rpkgs <- cv::rpackages
```

# Education, training, collaboration, and networking activities

<br>

## Activities within DDA

```{r list-teaching-dda}
cv_data %>% 
    filter(str_detect(organization, "Danish Diabetes Academy")) %>% 
    list_teaching("Courses taught for the DDA.") 
```
```{r list-committees}
list_committees(cv_data, "Committee for networking and education.")
```

## Activities outside DDA

### Teaching material in book format

```{r list-books}
list_publications(bib_items, "Books")
```

### Publications related to teaching

```{r list-articles}
bib_items %>% 
    filter(str_detect(title, "teaching|r-cubed")) %>% 
    list_publications("Journal articles") 
```

### Presentations related to teaching

```{r list-presentations}
bib_items %>% 
    filter(str_detect(title, "[tT]each|r-cubed")) %>% 
    list_publications("presentations")
```

### Educational activities as teacher or instructor

```{r list-teaching-not-dda}
cv_data %>% 
    filter(str_detect(organization, "Danish Diabetes Academy", negate = TRUE)) %>% 
    list_teaching() 
```
### Supervising students

```{r list-supervision}
list_supervision(cv_data)
```


### Curriculum development (archived with DOI)

```{r list-curriculum-archived}
list_publications(bib_items, "Curriculum development")
```

### Other curriculum development

```{r list-curriculum}
list_curriculum_development(cv_data)
```

### Teaching affiliations

```{r list-affiliations}
cv_data %>% 
    filter(str_detect(role, "[iI]nstructor|[tT]eacher")) %>% 
    list_affiliations()
```

### Educational certificates and courses taken

```{r}
cv_data %>% 
    arrange(desc(start)) %>% 
    filter(section %in% c("courses taken", "certificates"),
           str_detect(title, "Teacher|Instructor")) %>% 
    tidy_dates() %>%
        vitae::detailed_entries(
            what = title,
            when = date_range,
            with = organization,
            where = location
        ) %>% 
    output()
```

