---
title: "CV"
author: "Luke W. Johnston"
name: Luke
surname: Johnston
position: Postdoctoral researcher
address: Aarhus, Denmark
date: "`r cv::today_timestamp()`"
# profilepic: A local file path to an image
www: lukewjohnston.com
email: lwjohnst@gmail.com
#twitter: lwjohnst
github: lwjohnst86
aboutme: I am a diabetes epidemiologist, R user and programmer, teacher of modern data analysis skills, and open science advocate.
headcolor: "324ea8"
docname: "curriculum vitae"
csl: vancouver.csl
output:
    pagedown::html_resume:
        # set it to true for a self-contained HTML page 
        # but it'll take longer to render
        keep_md: yes
        self_contained: false
    vitae::awesomecv: 
        keep_tex: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    warning = FALSE,
    message = FALSE,
    results = "asis",
    comment = ""
)
# library(cv)
library(here)
devtools::load_all()
library(tidyverse)
library(RefManageR)
RefManageR::BibOptions(
    bib.style = "authoryear",
    first.inits = TRUE,
    style = "markdown",
    max.names = Inf,
    sorting = "ydnt"
    # no.print.fields = NULL
)
cv_data <- read_cv_items() 
bib_items <- read_bib_items() 
rpkgs <- cv::rpackages
```

## Education {data-icon=graduation-cap data-concise=true}

```{r list-education}
list_education()
```

## Publications {data-icon=file-alt}

```{r list-articles}
list_publications(bib_items, "Journal articles")
```

## Oral presentations

```{r list-orals}
list_publications(bib_items, "Oral presentations")
```

## Oral poster presentations

```{r list-oral-posters}
list_publications(bib_items, "Oral poster presentations")
```

## Poster presentations

```{r list-posters}
list_publications(bib_items, "Poster presentations")
```

## Other conference presentations

```{r list-other-conferences}
list_publications(bib_items, "Other conference presentations")
```

## Panel member

```{r list-panel-member}
list_publications(bib_items, "Panel member")
```

## Published R packages {data-icon=laptop-code}

```{r list-r-packages}
list_rpackages(rpkgs) 
```

## Teaching Experience {data-icon=chalkboard-teacher}

```{r list-teaching}
list_teaching(cv_data)
```

## Supervision Experience {data-icon=hands-helping}

```{r list-supervision}
list_supervision(cv_data)
```

## Curriculum Development (archived with DOI) {data-icon=university}

```{r list-curriculum-archived}
list_publications(bib_items, "Curriculum development")
```

## Other Curriculum Development {data-icon=university}

```{r list-curriculum}
list_curriculum_development(cv_data)
```

## Awards {data-icon=trophy}

```{r list-awards}
list_awards(cv_data)
```

## Employment {data-icon=suitcase}

```{r list-employment}
list_employment(cv_data)
```
