---
title: "CV"
author: "Luke W. Johnston"
name: Luke
surname: Johnston
position: Postdoctoral researcher
address: Aarhus, Denmark
date: "`r Sys.Date()`"
# profilepic: A local file path to an image
www: lukewjohnston.com
email: lwjohnst@ph.au.dk
twitter: lwjohnst
github: lwjohnst86
aboutme: I am a diabetes epidemiologist, R user and programmer, teacher of modern data analysis skills, and open science advocate.
headcolor: "324ea8"
docname: "curriculum vitae"
output:
    vitae::awesomecv:
        keep_tex: true
    pagedown::html_resume:
        # set it to true for a self-contained HTML page but it'll take longer to render
        self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    warning = FALSE,
    message = FALSE,
    results = "asis",
    comment = ""
)
# library(cv)
devtools::load_all()
library(tidyverse)
cv_data <- read_cv_items()
```

<!--
Aside
================================================================================


![Luke W. Johnston](https://avatars0.githubusercontent.com/u/6662983?s=460&v=4){width=80%}


Contact Info {#contact}
--------------------------------------------------------------------------------

- <i class="fa fa-envelope"></i> lwjohnst@gmail.com
- <i class="fa fa-twitter"></i> [twitter.com/lwjohnst](https://twitter.com/lwjohnst)
- <i class="fa fa-github"></i> [github.com/lwjohnst86](https://github.com/lwjohnst86)
- <i class="fa fa-gitlab"></i> [gitlab.com/lwjohnst](https://gitlab.com/lwjohnst)
- <i class="fa fa-stack-overflow"></i> [StackOverflow](http://stackoverflow.com/users/2632184)
- <i class="fa fa-stack-exchange"></i> [Stack Exchange](https://stackexchange.com/users/1992995)
- <i class="fa fa-linkedin-square"></i> [LinkedIn](https://www.linkedin.com/in/luke-johnston-480365101/)
- For more information, please contact me via email.

# Skills {#skills}

- Languages: English (fluent), Spanish (competent)
- Programming: Fluent in R, LaTeX, HTML, CSS, Bash, Git; familiar with 
SAS, Python.
- Statistical techniques: Basic (t-test, ANOVA, correlation), regression
modeling (linear, logistic), mixed effect modeling, generalized estimating
equations, principal component analysis, partial least squares regression, cross
validation, cluster analysis (hierarchical, k-means), information criterion
(AIC, QIC), bootstrapping, factor analysis.
-->

<!--
Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

Last updated on `r Sys.Date()`.


Main
================================================================================

Luke W. Johnston {#title}
--------------------------------------------------------------------------------
-->

# Education {data-icon=graduation-cap data-concise=true}

```{r list-education}
list_education()
```

# Publications and Posters {data-icon=file}

## Publications

```{r list-articles}
list_publications("Journal articles")
```

## Oral presentations

```{r list-orals}
list_publications("^Oral presentations")
```

## Oral poster presentations

```{r list-oral-posters}
list_publications("^Oral poster presentations")
```

## Poster presentations

```{r list-posters}
list_publications("Poster presentations")
```

## Other conference presentations

```{r}
list_publications("Other conference presentations")
```

## Panel member

```{r}
list_publications("Panel member")
```

# Published R packages {data-icon=cube}

```{r list-r-packages}
list_rpackages() 
```

# Teaching Experience {data-icon=chalkboard-teacher}

```{r list-teaching}
cv_data %>% 
    filter(section == "teaching") %>% 
    arrange(desc(start)) %>% 
    mutate(
        start = lubridate::year(start),
        end = lubridate::year(end),
        end = if_else(is.na(end), "present", as.character(end)),
        organization = organization %>% 
            str_replace_all("\\[(.+?)\\]\\(.+?\\)", "\\1")
    ) %>% 
    vitae::detailed_entries(
        what = glue("{str_to_sentence(role)} for {title}"),
        when = glue("{start}-{end}"),
        with = organization,
        where = location
    ) 

# ### {what}
# {with}
# {when}
# {where}
```

# Curriculum Development {data-icon=chalkboard-teacher}

```{r list-curriculum}
cv_data %>% 
    filter(section == "curriculum") %>% 
    arrange(desc(start)) %>% 
    mutate(
        start = lubridate::year(start),
        end = lubridate::year(end),
        end = if_else(is.na(end), "present", as.character(end))
    ) %>% 
    vitae::brief_entries(
        what = glue("{title} (link: {website})"),
        when = glue("{start}-{end}"),
        with = "",
    ) 

list_publications("Curriculum development")
# ### {what}
# {with}
# {when}
# {where}
```

# Awards

```{r list-awards}
list_awards(cv_data)
```

# Employment {data-icon=suitcase}

```{r list-employment}
list_employment(cv_data)
```
