---
title: ""
date: "`r cv::today_timestamp()`"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(cv)
```

- <i class="fa fa-envelope"></i> lwjohnst@gmail.com
- <i class="fa fa-twitter"></i> [twitter.com/lwjohnst](https://twitter.com/lwjohnst)
- <i class="fa fa-github"></i> [github.com/lwjohnst86](https://github.com/lwjohnst86)
- <i class="fa fa-gitlab"></i> [gitlab.com/lwjohnst](https://gitlab.com/lwjohnst)
- <i class="fa fa-stack-overflow"></i> [StackOverflow](http://stackoverflow.com/users/2632184)
- <i class="fa fa-stack-exchange"></i> [Stack Exchange](https://stackexchange.com/users/1992995)
- <i class="fa fa-linkedin-square"></i> [LinkedIn](https://www.linkedin.com/in/luke-johnston-480365101/)
- For more information, please contact me via email.

> I am a diabetes epidemiologist, R user and programmer, teacher of modern data analysis skills, and open science advocate.

### Skills

- Languages: English (fluent), Spanish (competent)
- Programming: Fluent in R, LaTeX, HTML, CSS, Bash, Git; familiar with 
SAS, Python.
- Statistical techniques: Basic (t-test, ANOVA, correlation), regression
modeling (linear, logistic), mixed effect modeling, generalized estimating
equations, principal component analysis, partial least squares regression, cross
validation, cluster analysis (hierarchical, k-means), information criterion
(AIC, QIC), bootstrapping, factor analysis.

```{r insert-cv, child="cv.Rmd"}
```
